Summary Tables

### 2020-02-24 summary_tables.Rmd
Add datasets of true distances
Use qualified scen names

  df <- io[[city]]$true_dist
  print(kable(df, caption = paste("True distance by mode for  ", city)))
}

>>>>

  df <- io[[city]]$true_dist

  names(df)[-1] <- lapply(append('baseline', rownames(scen_prop)), as.character)

  readr::write_csv(df, paste0('results/multi_city/true_distances/true_distance_', city, '.csv'))

  print(kable(df, caption = paste("True distance by mode for  ", city)))
}
